---
title: "Measured Disease Data"
author: "LRA"
date: "1/24/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
Region_order <- c("Alaska","British Columbia","Washington","Oregon","Bodega Bay","San Diego")
Region_order2 <- c("AK","BC","WA","OR","BB","SD")
```

## Wasting Disease Data 

This is an analysis of wasting disease prevalence and severity from the NSF surveys in 2019, as available in Jan 2020.

We are still working on getting the splits done in EELISA. However, the majority of the data are here.

```{r data, echo=FALSE}
disease_summ1 <- read.csv("Measured_Disease_summ.csv")
disease_summ2 <- read.csv("Measured_Disease_summ2.csv")
disease_summ1$Region <- ordered(disease_summ1$Region,levels=Region_order2)
disease_summ2$Region <- ordered(disease_summ2$Region,levels=Region_order2)
format(disease_summ2,digits=2)
```

### Transect-level prevalence

```{r prevalence, echo=FALSE}

ggplot(data=disease_summ1,aes(x=Region,y=prev,fill=TidalHeight))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2,position=position_dodge(width=0.75),
               show.legend = FALSE)+
  geom_text(data=disease_summ2,aes(x=Region,y=1.1,label=count),position=position_dodge(width=0.75))+
  scale_y_continuous(limits=c(0,1.12),breaks=c(0,0.25,0.5,0.75,1.0))+
  scale_fill_manual(values=c("wheat4","wheat3"))+
  ylab("Wasting Disease Prevalence")+
  xlab("Region")+
  labs(title="Wasting Disease Prevalence",
       subtitle = "Transect-level means, n=15-18 transects per region")+
  theme_bw()+
  theme()
```

### Transect-level severity


```{r severity, echo=FALSE}
ggplot(data=disease_summ1,aes(x=Region,y=sev,fill=TidalHeight))+geom_boxplot()+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2,show.legend=FALSE,
               position=position_dodge(width=0.75))+
  geom_text(data=disease_summ2,aes(x=Region,y=0.52,label=count),position=position_dodge(width=0.75))+
  scale_y_continuous(limits=c(0,0.52),breaks=c(0,0.1,0.2,0.3,0.4,0.5))+
  scale_fill_manual(values=c("wheat4","wheat3"))+
  ylab("Wasting Disease Severity")+
  labs(title="Wasting Disease Severity",
       subtitle = "Transect-level means, n=15-18 transects per region")+
  theme_bw()+
  theme()
```

### Transect-level prevalence, broken down by site
```{r site_prevalence, echo=FALSE}
ggplot(data=disease_summ1,aes(x=SiteCode,y=prev,color=TidalHeight))+
  geom_point(position=position_dodge(width=0.75))+
  facet_wrap(~Region)+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2,color="black",
               show.legend=FALSE,position=position_dodge(width=0.75))+
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.25,0.5,0.75,1.0))+
  scale_color_manual(values=c("wheat4","wheat3"))+
  ylab("Wasting Disease Prevalence")+
  labs(title="Wasting Disease Prevalence",
       subtitle="Transect-level means, n=3 transects per tidal height per site")+
  theme_bw()+
  theme(strip.background = element_rect(fill="white"))

```

### Transect-level severity, broken down by site
```{r site_severity, echo=FALSE}
ggplot(data=disease_summ1,aes(x=SiteCode,y=sev,color=TidalHeight))+
  geom_point(position=position_dodge(width=0.75))+
  facet_wrap(~Region)+
  stat_summary(fun.y=mean,geom="point",shape=8,size=2,color="black",
               show.legend=FALSE,position=position_dodge(width=0.75))+
  scale_y_continuous(limits=c(0,0.5),breaks=c(0,0.1,0.2,0.3,0.4,0.5))+
  scale_color_manual(values=c("wheat4","wheat3"))+
  xlab("Site Code")+
  ylab("Wasting Disease Severity")+
  labs(title="Wasting Dieseae Severity",
       subtitle = "Transect-level means, n=3 transects per tidal height per site")+
  theme_bw()+
  theme(strip.background = element_rect(fill="white"))
```